### 2018-04-10 paper.Rmd
gender plot changes

### Gender

```{r warning=FALSE}
stats <- get_speaker_statistics(role = "Target_Child")

data <- stats %>%
  filter(!is.na(target_child_sex), language == "eng") %>%
  group_by(target_child_id, target_child_age, target_child_sex, language) %>%
  summarise(measure = mean(mtld))

ggplot(data, aes(x = target_child_age, y = measure, color = target_child_sex)) +
  geom_smooth()
```

>>>>

### Gender
```{r}
stats <- get_speaker_statistics(role = "Target_Child")
```

```{r warning=FALSE}
lang_threshold <- 575
age_max <- 4

lang_counts <- stats %>% 
  filter(target_child_age < age_max * 365) %>%
  group_by(language) %>%

  summarise(n = n())

included_languages <- filter(lang_counts, n > lang_threshold)$language

data <- stats %>%
  filter(!is.na(target_child_sex), 
         language %in% included_languages) %>%
  group_by(target_child_id, target_child_age, target_child_sex, language) %>%
  filter(mtld != 0) %>%
  summarise(measure = mean(mtld)) %>%
  ungroup() %>%
  mutate(age_years = target_child_age / 365, 
         target_child_sex = factor(target_child_sex, levels = c("male","female"))) %>%
  filter(age_years < age_max)

mod <- lme4::lmer(measure ~ target_child_sex * poly(age_years, 2) - 1 + 
                    (1 | target_child_id) +
                    (target_child_sex + age_years | language), 
  data = data)

mod_data <- expand.grid(age_years = seq(0,age_max, .1), 
                                          target_child_sex = c("male","female"),
                                          language = included_languages) %>%
  as_data_frame()

mod_data$measure <- predict(mod, newdata = mod_data, 
                           re.form = ~(target_child_sex + age_years | language))

ggplot(data, aes(x = age_years, y = measure, 
                 color = target_child_sex)) +
  geom_point(alpha = .3) + 
  geom_line(data = mod_data, 
            aes(x = age_years, y = measure, color = target_child_sex)) +
  # geom_smooth(span = 1, method = "loess") + 
  facet_wrap(~language) + 
  ggthemes::theme_few() + 
  ggthemes::scale_color_ptol(name = "Sex") + 
  xlim(0,age_max) + 
  ylim(0,15) + 
  xlab("Age (years)") + 
  ylab("MTLD") + 
  theme(legend.position = "bottom")
```
